%-------------------------
% Resume in Latex
% Author : Imran Ariffin (forked from https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

  \usepackage{latexsym}
  \usepackage[empty]{fullpage}
  \usepackage{titlesec}
  \usepackage{marvosym}
  \usepackage[usenames,dvipsnames]{color}
  \usepackage{verbatim}
  \usepackage{enumitem}
  \usepackage[hidelinks]{hyperref}
  \usepackage{fancyhdr}
  \usepackage[english]{babel}
  
  \pagestyle{fancy}
  \fancyhf{} % clear all header and footer fields
  \fancyfoot{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
  
  % Adjust margins
  \addtolength{\oddsidemargin}{-0.5in}
  \addtolength{\evensidemargin}{-0.5in}
  \addtolength{\textwidth}{1in}
  \addtolength{\topmargin}{-.5in}
  \addtolength{\textheight}{1.0in}
  
  \urlstyle{same}
  
  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}
  
  % Sections formatting
  \titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
  
  %-------------------------
  % Custom commands
  \newcommand{\resumeItem}[2]{
    \item\small{
      \textbf{#1}{#2 \vspace{-2pt}}
    }
  }
  
  \newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
      \end{tabular*}\vspace{-5pt}
  }
  
  \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
  
  \renewcommand{\labelitemii}{$\circ$}
  
  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
  
  %-------------------------------------------
  %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
  
  \begin{document}
  
  %----------HEADING-----------------
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{http://imranariffin.github.io/}{\Large Imran Ariffin}} & Email : \href{mailto:ariffin.imran@gmail.com}{ariffin.imran@gmail.com}\\
    \href{http://imranariffin.github.io/}{http://www.imranariffin.github.io} & Mobile : 647-863-7073 \\
  \end{tabular*}
  
  
  %-----------EDUCATION-----------------
  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {University of Toronto}{Toronto, ON}
        {Bachelors of Applied Science in Computer Engineering}{Sept. 2013 -- Nov. 2017}
    \resumeSubHeadingListEnd
  
  
  %-----------EXPERIENCE-----------------
  \section{Industry Experience}
    \resumeSubHeadingListStart

      \resumeSubheading
        {Freckle - Killi}{Toronto, ON}
        {Full Stack Engineer}{Nov 2018 - Present}
        \resumeItemListStart
          \resumeItem{}
            {Caught and fixed a multihtreaded issue left unsolved causing production issues for months, among others, improving the stability of the whole system}
          \resumeItem{}
            {Maintained and improved legacy system while being the key knowledge resource for migrating to a new system}
          \resumeItem{}
            {Mentored peers and juniors in pair programming and code reviews to get them ready to contribute to the legacy and new system, helping the team grow}
          \resumeItem{}
            {Become a key resource for product and business in anything related to the system end to end}
        \resumeItemListEnd
  
      \resumeSubheading
        {Scotiabank Wealth Rapid Lab - Client On-boarding}{Toronto, ON}
        {Software Engineer}{Jan 2018 - Oct 2018}
        \resumeItemListStart
          \resumeItem{}
            {Always ready to jump in to, quickly investigate and resolve production issues by analyzing the logs and database as well as quick technical discussions with other developers resulting in average resolution time of 3 days.}
          \resumeItem{}
            {Implemented redux middleware to send browser errors back to the server providing deeper insights in production issues investigation.}
          \resumeItem{}
            {Improved the UI by refactoring for iPad and iPhone enabling better accessibility for clients to onboard.}
          \resumeItem{}
            {Implemented automatic logout on session token timeout resulting in better user experience.}
        \resumeItemListEnd
  
      \resumeSubheading
        {Department of Economics, University of Toronto}{Toronto, ON}
        {Data Visualization Research Assistant}{May 2017 - Sept 2017}
        \resumeItemListStart
          \resumeItem{}
            {Developed an interactive web-based frequency polar chart enabling providing a way for researchers to see trends from past to current. Implemented using React, Highcharts and Express for client-server architecture and Python for data parsing.}
        \resumeItemListEnd
  
      \resumeSubheading
        {Dealters.my}{Kuala Lumpur, Malaysia}
        {Fullstack Engineer Intern}{May 2015 - Sept 2015}
        \resumeItemListStart
          \resumeItem{}
            {Bootstrapped the backend server using Nodejs, Express, Facebook login and Mongodb, leading to the launch of the web application on Heroku.}
          \resumeItem{}
            {Cooperated closely with front-end engineer and designer to design the API and products schema.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


  %-----------OPEN SOURCE CONTRIBUTIONS-----------------
  \section{Open source contribution}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Project Iodide}{github.com/iodide-project/iodide}
        {Started to actively participate during Pycon 2019 Sprint @ Mozilla and planning to continue}{}
        \resumeItemListStart
          \resumeItem{}
            {Developed new features including enabling user to clear their console history with a click and introducing a new command to download obejcts as bytes}
          \resumeItem{}
            {Fixed two bugs thus far}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


  %-----------PROJECTS-----------------
  \section{Projects}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Small Steps}{github.com/imranariffin/small-steps}
        {A mobile app to list down your ambitious goals and break down to smallest actionable tasks}{}
        \resumeItemListStart
          \resumeItem{}
            {Designed and developed minialist UI for the React Native application}
          \resumeItem{}
            {Carefully unit tested the code with high coverage}
        \resumeItemListEnd
      \resumeSubheading
        {liveSWOT.com}{www.liveswot.com/}
        {A platform to collaborate on your SWOT analysis with your team mates in real time}{}
        \resumeItemListStart
          \resumeItem{}
            {Designed and developed material UI for the Redux-React application using Material design.}
          \resumeItem{}
            {Designed and developed RESTful API endpoints using Django Rest Framework and PostgreSQL.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
  
  %
  %--------PROGRAMMING SKILLS------------
  %\section{Programming Skills}
  %  \resumeSubHeadingListStart
  %    \item{
  %      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
  %      \hfill
  %      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
  %    }
  %  \resumeSubHeadingListEnd
  
  
  %-------------------------------------------
  \end{document}
  